Explorative Data Analysis Climate Perceptions in Countries

### 2022-11-27 Code/Final_Exploratory_Analysis_CAP_DAP.Rmd
feedback on data exploration and draft analysis

## Emitting the Last Two Rows
```{r}
emissions <- emissions %>% slice(-194,-195)
# Gets rid of the last two rows.
```

@@

@@

emissions<- cbind(emissions1, emissionsfix)
```
NA's were introduced by coercion into the countries that have FALSE listed as their emissions, because their emissions could not be recorded.

@@

emissions_US_Denmark$year<- 'NA'
emissions_US_Denmark$year<- as.numeric(emissions_US_Denmark$year)
emissions_US_Denmark[1:30,2]<-1990:2019
emissions_US_Denmark[31:60,2]<- 1990:2019
```
 str_replace
 str_detect
 str_split 
 Feel free showing me the other way

@@

@@

Now time for a Boxplot

@@

@@

@@

```{r}
as.vector(as.character((yale[1,])))
#make a vector of the character data in row one of yale
#??? not sure why this code is also needed up here, when I deleted it, it did not work.???
ccs_Yale_Corrected<- yale %>% slice(-1)
#remove row one of yale and store it as a new data frame
names(ccs_Yale_Corrected)<-c(as.vector(as.factor((yale[1,]))))
#make the column names of the new data frame a vector of the character data in row one of yale
```

>>>>

## Omitting the Last Two Rows
```{r}
emissions <- emissions %>% slice(-194,-195)
# Gets rid of the last two rows.
```

@@

If you dropped `stringsAsFactor = T` when you read in the data you can save yourself a big headache here. There are two issues:

1. R won't allow column names that are numbers so it adds the X. This does not change the data type to factor- but it makes it difficult to use the numeric information in the dates.

2. Because the folks who created the data used FALSE in some of the year columns, instead of NA (which R recognizes), R interprets those columns as character data (or, in this case, factor, because you imported with stringsAsFactors = T)

@@

emissions<- cbind(emissions1, emissionsfix)
```
Well done! I'm not sure this was the easiest route, but you figured it out!

NA's were introduced by coercion into the countries that have FALSE listed as their emissions, because their emissions could not be recorded.

@@

emissions_US_Denmark$year<- 'NA'
emissions_US_Denmark$year<- as.numeric(emissions_US_Denmark$year)
emissions_US_Denmark[1:30,2]<-1990:2019
emissions_US_Denmark[31:60,2]<- 1990:2019
```
The trouble with your way is that it cannot be automated, and is thus more prone to user error. It would also be increasingly more difficult with larger and larger data sets.

You could try this (my demo is with emissions_long)

```{r}
erika_demo<- emissions_long
erika_demo$year<-str_replace(erika_demo$year, "X", "")
erika_demo$year<-as.numeric(erika_demo$year)
```

 str_replace
 str_detect
 str_split 
 Feel free showing me the other way
 See above

@@

It works when I do it - not sure the issue. And I'm not sure you want method = "lm" because these are not linear plots.

@@

I wonder if it would be interesting to find the population size of USA and Denmark in all of those years and then calculate emissions per capita - Denmark will always have lower emissions than the US because it is a smaller country.

Another option, which I discussed with professor Lock in Stats, is to look at the RATE of emissions change from year to year since the rate of change is independent of population size.

Think about how you would calculate the rate of change.
Now time for a Boxplot

@@

How many of the Facebook questions are you going to examine?

@@

You have character data you mean, not factor.

@@

```{r}
as.vector(as.character((yale[1,])))
#make a vector of the character data in row one of yale
#??? not sure why this code is also needed up here, when I deleted it, it did not work.???
ccs_Yale_Corrected<- yale %>% slice(-1)
#remove row one of yale and store it as a new data frame
names(ccs_Yale_Corrected)<-c(as.vector(as.factor((yale[1,]))))
#make the column names of the new data frame a vector of the character data in row one of yale
```
You made this more complicated than it needed to be, but it worked. Here's another, easier way.

```{r}
erika_demo2 <- yale
goodNames<-slice(erika_demo2, 1) %>% unlist(use.names = FALSE)
names(erika_demo2)<-goodNames
erika_demo2<-erika_demo2[2:nrow(erika_demo2),]
```
